
---
title: "Respirometry Trails for Summer Krill 2019"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: journal
    highlight: zenburn
    smart: false

---


Hello World

Author: OA Lab, NWFSC
Title: Respirometry Trails for Summer Krill 2019
Date: November 2020


placeholder

```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```

placeholder

```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(purrr)
library(wql)
library(lubridate)
library(arsenal)
#for graphing
library(ggplot2)
library(stringr)
library(nlme)
library(RColorBrewer)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```


placeholder 

#*********************************
## Outline Current (2020.10.30)
#*********************************

## 1.) Working Directory
## 2.) Creating the Out-files
## 3.) Reformatting directory to correct format 
## 4.) Analysis 

## 5.) Placeholder 
## 6.) Placeholder
## 7.) Placeholder
## 8.) Placeholder
## 9.) Placeholder
## 10.) Placeholder


```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometry")
```



placeholder

```{r 3.) Creating the Dataframe, dRESP, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 3.) Creating the Dataframe, dRESP
#*********************************

## Method 1 - 1 file for the four trials
#get all the files in the defined working directory that are in csv format
dRESP <- read.csv(file = "KRILL_Resp_alltrials.csv", stringsAsFactors = FALSE)
dim(dRESP)

write.csv(dRESP, file = "2020.11.04_presenseSENSORONLY.alltrials.data.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# dRESPanimal represents just the animal, vial, MOATs, etc.  
dRESPanimal <- read.csv(file = "RespirometryTrials_all.Animal.Info.csv") 
dim(dRESPanimal)

write.csv(dRESPanimal, file = "2020.11.04_krillanimaldata.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


#dRESPmsr represents the measurements made by the presense optical device for Dissolved Oxygen 
dRESPmsr <- merge(dRESP, dRESPanimal, by="SensorName")

write.csv(dRESPmsr, file = "2020.11.04_respirometrymeasurements.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


dRESP$MOATS <- factor(dRESP$MOATS)
# Checking the names of the different levels
levels(dRESP$MOATS)


```




placeholder





placeholder





placeholder





placeholder



























```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

