
---
title: "Respirometry Trails for Summer Krill 2019"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: journal
    highlight: zenburn
    smart: false

---


Hello World

Author: OA Lab, NWFSC
Title: Respirometry Trails for Summer Krill 2019
Date: November 2020


placeholder

```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```

placeholder

```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(purrr)
library(wql)
library(lubridate)
library(arsenal)
library(compareDF)
#for graphing
library(ggplot2)
library(stringr)
library(nlme)
library(RColorBrewer)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```


placeholder 
# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometry")
```



placeholder
# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, dRESP, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the intial Dataframe, dRESP
#*********************************

## Method 1 - 1 file for the four trials
#get all the files in the defined working directory that are in csv format
dRESP <- read.csv(file = "KRILL_Resp_alltrials.csv", stringsAsFactors = FALSE)
dim(dRESP)

write.csv(dRESP, file = "2020.11.06_presenseSENSORONLY.alltrials.data.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# dRESPanimal represents just the animal, vial, MOATs, etc.  
dRESPanimal <- read.csv(file = "RespirometryTrials_all.Animal.Info.csv") 
dim(dRESPanimal)

write.csv(dRESPanimal, file = "2020.11.06_krillanimaldata.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


#dRESPmsr represents the measurements made by the presense optical device for Dissolved Oxygen 
dRESPmsr <- merge(dRESP, dRESPanimal, by="SensorName")

write.csv(dRESPmsr, file = "2020.11.06_respirometrymeasurements.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# dRESP$MOATS <- factor(dRESP$MOATS)
# Checking the names of the different levels
# levels(dRESP$MOATS)


```




placeholder
# 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects }

#*********************************
## 3.) Creating dateTime objects  
#*********************************

dRESPmsr$dateTime <- ""
dRESPmsr$dateTime <- as.POSIXct(paste(dRESPmsr$Date,
                                      dRESPmsr$Time), "%d-%B-%y %H:%M:%S", tz="UTC")

# QA check
dim(dRESPmsr)

dRESPmsr$Time <- as.POSIXct(dRESPmsr$dateTime, format="%H:%M:%S")


```



# 4.) Cleaning up observations
```{r 4.) Cleaning up observations }
#*********************************
## 4.) Cleaning up observations  
#********************************

#Removing items with faulty sensor names
dRESPmsr <- subset(dRESPmsr, SensorName != "")

dRESPmsr$SensorName <- str_trim(dRESPmsr$SensorName, side = c("both"))
dRESPmsr$SensorName <- factor(dRESPmsr$SensorName)
dim(dRESPmsr)

dRESPmsr <- subset(dRESPmsr, Value != "---")

# Confirming proper number of krill 
# 76, 4x19 propoer number of animals under observation 
unique(dRESPmsr$SensorName)
UniqueSensorNames <- levels(dRESPmsr$SensorName)
write.table(UniqueSensorNames, file = "2020.11.06DRESPmsr_UniqueSensorNames.csv")
kable(UniqueSensorNames)

```

placeholder
## 4.a) Plot to demonstrate the SensorName
```{r 4.a) Plot to demonstrate the SensorName echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 4.a) Plot to demonstrate the SensorName 
#*********************************

# ggplot(dRESPmsr, aes(x = Time, y = Value, colour = SensorName)) +
#   geom_point(size = 1) +
#   geom_smooth(method = "lm") + 
#   #scale_y_continuous(breaks=seq(250,950,by=50))   +
#   theme_bw()

```

placeholder


placeholder

#5.) Creating Trial ID & Krill ID
```{r 5.) Creating Trial ID & Krill ID}
#*********************************
## 5.) Creating a Krill ID with Trial in name    
#*********************************

## First Trial began at 2019-10-28 14:25:01
## First Trial ended at 2019-10-28 16:37:29

## Second Trial began at 2019-10-28 18:55:21
## Second Trial ended at 2019-10-28 21:16:45

## Third Trial began at 2019-10-29 14:06:21
## Third Trial ended at 2019-10-29 16:18:36

## Fourth Trial began at 2019-10-29 17:20:21
## Fourth Trial ended at 2019-10-29 19:32:01


dRESPmsr$TrialID <- ""
dRESPmsr <- dRESPmsr %>% mutate(TrialID=case_when(
  
## First Trial began at 2019-10-28 14:25:01
## First Trial ended at 2019-10-28 16:37:29
  
  ((Time >= as.POSIXct("2019-10-28 14:25:00", tz = "UTC")) 
   & (Time < as.POSIXct("2019-10-28 16:37:30", tz = "UTC"))) ~ "Trial01",

  
## Second Trial began at 2019-10-28 18:55:21
## Second Trial ended at 2019-10-28 21:16:45  
  
  ((Time >= as.POSIXct("2019-10-28 18:55:20", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-28 21:16:50", tz = "UTC"))) ~ "Trial02",


## Third Trial began at 2019-10-29 14:06:21
## Third Trial ended at 2019-10-29 16:18:36


  ((Time >= as.POSIXct("2019-10-29 14:06:18", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-29 16:18:40", tz = "UTC"))) ~ "Trial03",

## Fourth Trial began at 2019-10-29 17:20:21
## Fourth Trial ended at 2019-10-29 19:32:01

  
  ((Time >= as.POSIXct("2019-10-29 17:20:18", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-29 19:40:01", tz = "UTC"))) ~ "Trial04",

  TRUE ~"other"
)) 

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## new value 
## dRESPmsr$KrillID

dRESPmsr$KrillID <- ""

dRESPmsr$KrillID <- paste(dRESPmsr$TrialID, "_", dRESPmsr$SensorName, sep="")
#View(dRESPmsr)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```


placeholder

# 6.) DO Corrections
```{r 6.) DO trial 3 correction applied to all rounds}
#*********************************
## 6.) DO trial 3 correction applied to all rounds   
#*********************************

# New values to correct the DO values for the temperature in Trial 3 in the dataframe dRESPmsr

dRESPmsr$percentDOassumpt <- ""
dRESPmsr$assumedSatDOmg <- ""
dRESPmsr$percentDO <- ""
dRESPmsr$obseveredSatDOmg <- ""
dRESPmsr$actualDOmg <- ""

dRESPmsr$percentDOassumpt <- as.numeric(dRESPmsr$percentDOassumpt)
dRESPmsr$assumedSatDOmg <- as.numeric(dRESPmsr$assumedSatDOmg)
dRESPmsr$percentDO <- as.numeric(dRESPmsr$percentDO)
dRESPmsr$obseveredSatDOmg <- as.numeric(dRESPmsr$obseveredSatDOmg)
dRESPmsr$actualDOmg <- as.numeric(dRESPmsr$actualDOmg)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Correct Temperature
dRESPmsr$CorTemp <- 11

#Salinity Constant
dRESPmsr$SalinityConstant <- 30.3
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# Numeric Corrections to DO value
dRESPmsr$Value <- as.numeric(dRESPmsr$Value)

dRESPmsr$assumedSatDOmg <- oxySol(dRESPmsr$CorTemp, 
                                  dRESPmsr$SalinityConstant)

dRESPmsr$percentDOassumpt <- dRESPmsr$Value / dRESPmsr$assumedSatDOmg

dRESPmsr$obseveredSatDOmg <- oxySol(dRESPmsr$CorTemp, dRESPmsr$SalinityConstant)

dRESPmsr$percentDO <- dRESPmsr$Value / dRESPmsr$assumedSatDOmg

dRESPmsr$actualDOmg <- dRESPmsr$percentDO * dRESPmsr$obseveredSatDOmg


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
```


placeholder
# 6.a) DO table & DO correction Plot Check
```{r 6.a) DO table & DO correction Plot Check  }
#*********************************
## 6.a) DO table & DO correction Plot Check  
#*********************************

# write.table(dRESPmsr, file = "2020.11.06.dRESPmeasurements", sep=";", 
#             row.names = TRUE)
# 
# dRESPmsr <-subset(dRESPmsr, actualDOmg != "---")
# dRESPmsr$Time <- as.POSIXct(dRESPmsr$Time, format="%H:%M:%S")
# ggplot(dRESPmsr, aes(x = Time, y = actualDOmg, colour = SensorName)) +
#   geom_point(size = 1) +
#   geom_smooth(method = "lm") + 
#   facet_wrap(~TrialID) +
#   #scale_y_continuous(breaks=seq(250,950,by=50))   +
#   theme_bw()

```



placeholder
# 7.) Analysis, Respirometry - Creating the Slope Function 
```{r 7.) Analysis, Respirometry - Creating the Slope Function}
#*********************************
## 7.) Analysis, Respirometry - Creating the Slope Function  
#*********************************  

vialVol <- 28.06 #ml

oxygen <- vialVol * dRESPmsr$actualDOmg   

dRESPmsr$oxygen <- oxygen

#nmol/vial; conversion for L to ml and umol to nmol cancels


#slope funcion of 2 vectors
slope <- function(y,x){
  return(lm(y~x, na.action = na.omit)$coefficients[2])
}
  

dRESPmsr$delta_t <- as.numeric(dRESPmsr$delta_t)

cSlopes <- by(dRESPmsr, dRESPmsr$KrillID, function(x){ slope(x$oxygen, x$delta_t)})


#creating a data frame instead of a list 
ds <- as.data.frame(sapply(cSlopes, I))
#having row names be a variable in a column to be able to pull it out for later merging 
ds$TrialID<- row.names(ds)



```



placeholder
# 8.) Creating the ds dataframe
```{r 8.) Creating the ds dataframe}
#*********************************
## 8.) Creating the ds dataframe
#*********************************

#creating a data frame instead of a list 
ds <- as.data.frame(sapply(cSlopes, I))
#having row names be a variable in a column to be able to pull it out for later merging 
ds$TrialID<- row.names(ds)

dim(ds)

#add column to dslopes thats KrillID
#View(dref)
ds$KrillID <- row.names(ds)
#View(dslopes)
dtotal <- merge(dRESPmsr, ds, by = "KrillID")
View(dtotal)

unique(dtotal$KrillID)
UniqueKrillIDs <- levels(dtotal$KrillID)
write.table(UniqueKrillIDs, file = "2020.11.06dtotal_UniqueKrillIDs.csv")
kable(UniqueSensorNames)



```


placeholder
# 9.) Creating Slope Functions & Linear Models 
```{r 9.) Creating Slope Functions & Linear Models }
#*********************************
## 9.) Creating the ds dataframe
#*********************************
# #get slopes and r^2 values from dtotal - just adjusted code from data analysis to fit into these df's
dtotal$KrillID <- factor(dtotal$KrillID)
nlevels(dtotal$KrillID)

dtotal[is.na(dtotal$delta_t),]
unique(dtotal$KrillID)

#how best to run the lmlist over
# group and then run a function tidyverse
# group by krill ID and then run the function

levels(dtotal$KrillID)
GRP_dtotal <- dtotal %>% group_by(KrillID)
dtotal <- GRP_dtotal

```


##### 9.a Missing Slope Value
```{r 9.a Missing Slope Values}
info <- lmList(oxygen ~ delta_t|KrillID, dtotal,na.action=na.omit)
#view(dtotal[!dtotal$KrillID %in% names(info), ])

MissingINFOobservations <- (dtotal[!dtotal$KrillID %in% names(info), ])
dtotalVSmissinfo <- summary(comparedf(dtotal, MissingINFOobservations))

kable(MissingINFOobservations)
```



##### 9.b Exploring 3 Missing Observations
```{r 9.a IncludedSlope Values}

write.csv(MissingINFOobservations, file = "2020.11.16_MissingINFOobservations.csv", row.names = FALSE)

#Summary function commented out due to errors below

summary(comparedf(dtotal, MissingINFOobservations, by = "delta_t"))
#Resulting Faults
#...Non-identical attributes
#...No non-identical attributes


# summary.comparedf(dtotal, MissingINFOobservations, by = delta_t)

#kable(Incld_UniqueKrillIDs)

```


## 9.C Comparison between Krillr4_58 and 59 to better determine differences
Using neighboring observations to determine if any difference
```{r 9.C Comparison between Krillr4_58 and 59 to better determine differences}

dRESP_58 <- read.csv(file = "2020.11.16_REPRwork_KRLr4_58comparison.csv", stringsAsFactors = FALSE)
dRESP_59 <- read.csv(file = "2020.11.16_REPRwork_KRLr4_59comparison.csv", stringsAsFactors = FALSE)

comparedf(dRESP_58, dRESP_59)

# Compare Object
# 
# Function Call: 
# comparedf(x = dRESP_58, y = dRESP_59)
# 
# Shared: 52 non-by variables and 41 observations.
# Not shared: 0 variables and 9 observations.
# 
# Differences found in 10/52 variables compared.
# 0 variables compared have non-identical attributes.


comparedf(dRESP_58, dRESP_59, by = "delta_t")


```


## 9.d Comparing the slopes of 58 and 59 
```{r 9.d Comparing the slopes of 58 and 5}

GRP_dtotal 
write.csv(GRP_dtotal, file = "2020.11.16_GRP_dtotalObservations.csv", row.names = FALSE)


GRP_dtotal_58 <- read.csv(file = "2020.11.16_GRP_dtotalObservationsKRL4_58.csv", stringsAsFactors = FALSE)
GRP_dtotal_59 <- read.csv(file = "2020.11.16_GRP_dtotalObservationsKRL4_59.csv", stringsAsFactors = FALSE)


comparedf(dRESP_58, dRESP_59, by = "oxygen")

```





```{r}
summary(lm(oxygen ~ delta_t, data= dtotal[dtotal$KrillID=="Trial04_KRLr4_59",]))$r.squared

lm(oxygen ~ delta_t, data= dtotal[dtotal$KrillID=="Trial04_KRLr4_68",])

lm(oxygen ~ delta_t, data= dtotal[dtotal$KrillID=="Trial04_KRLr4_69",])


dtotal[is.na(dtotal$delta_t),]
unique(dtotal$KrillID)

names(info)

view(dtotal[!dtotal$KrillID %in% names(info), ])


print(info)

# slopes <- coef(info)[2]
# #print(slopes)
# dslopes <- data.matrix(slopes)
# #View(dref)
# mode(dslopes[,1])
# dslopes <- as.data.frame(dslopes)
# dslopes$slope <- dslopes$delta_t
# dslopes$delta_t <- NULL
# #View(dslopes)

#now for R^2!!
Rsq <- sapply(info,function(x) summary(x)$r.squared)
t(Rsq) #transposes rows and columns
Rsq <- data.matrix(Rsq)
#View(Rsq)
dtotal <- cbind(ds, Rsq)
View(dtotal)

```




















#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************

